Box 1 - TDT Curves

### 2023-09-19 ms/ms.qmd
Cleaning doc

---
title: "Box 1 - TDT Curves"
bibliography: ../bib/refs.bib
csl: ../bib/nature.csl
format:
  docx:
    reference-doc: ../bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
---

@@

```{r, tree}
# Bring in the fly tree
  tree <- read.tree(here::here("phylogeny/", "drosi2.tre"))

# Plot the tree
  plot(tree, cex = 0.2)

@@

# Grab out data
   data <- read.csv(here::here("data", "drosi_data.csv"))

@@

```{r, models}

### MCMCglmm Bayesian models. Deals with missing data using data augmentation

@@

```{r, posteriors}

# Extract posterior estimates
  sol <- mcmcglmm_model$Sol
  vcv <- mcmcglmm_model$VCV

@@

>>>>

---
title: "Box 1 - TDT Curves"
bibliography: ../bib/refs.bib
csl: ../bib/nature.csl
format:
  docx:
    reference-doc: ../bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: '**Figure**'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
---

@@

##################################
# Loading tree and data
##################################
# Bring in the fly tree
  tree <- read.tree(here::here("phylogeny/", "drosi2.tre"))

# Grab our data
   data <- read.csv(here::here("data", "drosi_data.csv"))
```

```{r, treesetup}
#| label: treesetup
#| echo: false
#| message: false
#| include: false

@@

@@

```{r, models}
#| label: models
#| echo: false
#| include: false
#| 
### MCMCglmm Bayesian models. Deals with missing data using data augmentation

@@

```{r, posteriors}
#| label: posteriors
#| echo: false
#| include: false
#| 
# Extract posterior estimates
  sol <- mcmcglmm_model$Sol
  vcv <- mcmcglmm_model$VCV

@@

```{r, fig-tree}
#| label: fig-tree
#| fig-cap: "Phylogenetic relationships among `r length(tree$tip.label)` *Drosophila* species."

# Plot the tree
  plot(tree, cex = 0.2)
```
